Solution of hydrodynamic equilibrium in black-oil reservoirs: the classical material balance equation

### 2014-10-07 pituba/article/article_spe.tex
petro changes

% Review
%\documentclass[authoryear,preprint,review,11pt]{elsarticle}
\documentclass[final,authoryear,5p,twocolumn,10pt]{elsarticle}

@@

After presenting the material balance equation, sufficient conditions are shown for which material balance equation has only one solution for pressure. These conditions require fluids to be compressible and gas vaporization to occur with increase of oil phase density. A simple scheme for numerical solution is also proposed based on classical root-finding algorithms for non-linear equations.

@@

Phase densities are functions of the local thermodynamic state:
\begin{equation}
\rho_w = \rho_w \left(p_w, T_w\right)
\end{equation}
\begin{equation}
\rho_o = \rho_o \left(p_o, T_o,Y_g\right)
\end{equation}
\begin{equation}
\rho_g = \rho_g \left(p_g, T_g\right)
\end{equation}

>>>>

% Review
\documentclass[authoryear,preprint,review,11pt]{elsarticle}
%\documentclass[final,authoryear,5p,twocolumn,10pt]{elsarticle}

@@

After presenting the material balance equation, sufficient conditions are shown for which the material balance equation has only one solution for pressure. These conditions require fluids to be compressible and gas vaporization to occur with increase of oil phase density. A simple scheme for numerical solution is also proposed based on classical root-finding algorithms for non-linear equations.

@@

Phase densities are functions of the local thermodynamic state:
\begin{equation}
\rho_w = \rho_w \left(p_w, T_w\right) \, ,
\end{equation}
\begin{equation}
\rho_o = \rho_o \left(p_o, T_o,Y_g\right) \, ,
\end{equation}
\begin{equation}
\rho_g = \rho_g \left(p_g, T_g\right) \, .
\end{equation}
